Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-02-06 paper/main.tex
Updates

\begin{enumerate}
	\item \textbf{Continuous:} We train a model, $ E_X: x \sim
		\bm{z} $. The residuals are then computed by taking the difference
		between the true and the predicted values using $ E_X $. 
		$$ R_{x_i} = x_i - E_X(\bm{z}_i) $$
	\item \textbf{Ordinal:} We start by training a probability estimator, $
		p_X: x \sim \bm{z} $, and then use the estimated probabilities, 
		$ \hat{p}_X(x) $ to compute the residuals:
		$$ R_{x_i} = \hat{p}_X(X < x_i) - \hat{p}_X(X > x_i) $$
	\item \textbf{Categorical:} We again start by training a probability
		estimator $ p_X: X \sim \bm{Z} $, and obtain probability
		estimates $ \hat{p}_X: p_X(\bm{Z}) $. Next, we dummy encode the
		categorical variable and then compute the residuals as follows: 
		$$ R_{x_i} = x_i - \hat{p}(\bm{z}_i) $$
\end{enumerate}

>>>>

\begin{enumerate}
	\item \textbf{Continuous:} We train a model, $ E_X: x \sim
		\bm{z} $. The residuals are then computed by taking the difference
		between the true and the predicted values using $ E_X $. 
		$$ R_{x_i} = x_i - E_X(\bm{z}_i) $$
	\item \textbf{Ordinal:} We start by training a probability estimator, $
		p_X: x \sim \bm{z} $, and then use the estimated probabilities, 
		$ \hat{p}_X(x) $ to compute the residuals:
		$$ R_{x_i} = \hat{p}_X(X < x_i) - \hat{p}_X(X > x_i) $$
	\item \textbf{Categorical:} We again start by training a probability
		estimator $ p_X: x \sim \bm{z} $, and obtain probability
		estimates $ \hat{p}_X: p_X(\bm{z}) $. Next, we dummy encode the
		categorical variable and then compute the residuals as follows: 
		$$ R_{x_i} = x_i - \hat{p}(\bm{z}_i) $$
\end{enumerate}
